\LARGE \bf Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving

### 2016-01-13 paper1.tex
added bibliography

@@

\usepackage[pdftex]{graphicx}
\usepackage[hypcap]{caption}

@@

It is obvious that there are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\bar{a}_m$ and $\bar{j}_m$.
The authors then propose that 4 other basic profiles be defined, and an algorithm constructed which judiciously chooses the appropriate profile for every segment defined by a vector $\bf{G}$.
The other profiles are explained below in section \ref{sec:jerkprofiles}.
A path is then a set of $N$ segments, each of which is defined by a set of parameters $G_i, i = 1 ... N$ and can be solved indivually in sequence.
Determination of where to break a path into segments is discussed below in Section \ref{sec:pathsegmentation}.

@@

The case mentioned above wherein the speed limit is too high for a solution to exist for a 7 phase profile. The middle travel period is removed, so that the vehicle increases speed and then immediately decreases speed. The peak speed in this case has a solution, but cannot be manipulated directly.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.6\columnwidth]{graphics/6phase_v(s).png}
  \caption{6 phase profile, displayed as speed vs. position along path}
  \label{fig:6phaseprofile}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.6\columnwidth]{graphics/4phase_v(s).png}
  \caption{4 phase profile, displayed as speed vs. position along path.}
  \label{fig:4phaseprofile}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.6\columnwidth]{graphics/4Rphase_all_derivatives.png}
  \caption{Reversed 4 phase profile, displayed as speed vs. position along path.}
  \label{fig:4rphaseprofile}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.6\columnwidth]{graphics/3phase_v(s).png}
  \caption{3 phase profile, displayed as speed vs. position along path.}
  \label{fig:3phaseprofile}
\end{figure}

@@

% make sure to incorporate extensibility to other constraints
asdf

@@

>>>>

\usepackage[pdftex]{graphicx}
\usepackage[hypcap]{caption}
\usepackage[noadjust]{cite}

@@

@@

It is obvious that there are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\bar{a}_m$ and $\bar{j}_m$.
The authors then propose that 4 other basic profiles be defined, and an algorithm constructed which judiciously chooses the appropriate profile for every segment defined by a vector $\bf{G}$.
The other profiles are explained below in section \ref{sec:jerkprofiles}.
A path is then a set of $N_s$ segments, each of which is defined by a set of parameters $G_k, k = 1 ... N_s$ and can be solved indivually in sequence.
Determination of where to break a path into segments is discussed below in Section \ref{sec:pathsegmentation}.

@@

In the case mentioned above, wherein the speed limit is too high for a solution to exist for a 7 phase profile, The middle travel period is removed, so that the vehicle increases speed and then immediately decreases speed. 
The peak speed in this case has a solution, but cannot be manipulated directly.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.7\columnwidth]{graphics/6phase_v(s).png}
  \caption{6 phase profile, displayed as speed vs. position along path}
  \label{fig:6phaseprofile}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.7\columnwidth]{graphics/4phase_v(s).png}
  \caption{4 phase profile, displayed as speed vs. position along path.}
  \label{fig:4phaseprofile}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.7\columnwidth]{graphics/4Rphase_all_derivatives.png}
  \caption{Reversed 4 phase profile, displayed as speed vs. position along path.}
  \label{fig:4rphaseprofile}
\end{figure}

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.7\columnwidth]{graphics/3phase_v(s).png}
  \caption{3 phase profile, displayed as speed vs. position along path.}
  \label{fig:3phaseprofile}
\end{figure}

To decide which profile to employ, a cascade approach is used. Analytic values of time intervals are evaluated for each profile by plugging in values of $\bar{G}$, $\bar{a}_m$, and $\bar{j}_m$ until all time intervals are positive and real. 
The order in which they are attempted is: 7 $\rightarrow$ 6 $\rightarrow$ 4 $\rightarrow$ 4R $\rightarrow$ 3.

@@

% make sure to incorporate extensibility to other constraints
The goal of the segmentation process is to divide a given path into multiple portions where each has a uniform upper limit on speed, acceleration, and braking.
After this is done, the process described above in Section \ref{sec:jerkprofiles} may be applied to each of the segments.

To begin, 5 values must be computed for each point in the planned path consisting of $N_p$ points: $v_{m,k}$, $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ for $k = 1, ... N_p$ . Each value is a minimax, i.e., a minimum of several maxima computed from various constraints. For instance, ...

For the purposes of this work, two constraints are used for $v_m$: legal speed limit (set constant for the whole path) and lateral acceleration limit. Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation $v_{m,k}(a_{B,y}) = \sqrt{a_{B,y}^{max}/\kappa_k}$ for $k = 1, ..., N_p$. For each path point, the value $v_{m,k}(a_{B,y})$ denotes the speed necessary to obtain the limit lateral acceleration, denoted by $a^{max}_{B,y}$. The value $\kappa_k$ denotes the path curvature at each point. For the sake of simplicity, the values of $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ are all set constant for the entire path, using recommendations from \cite{Maurya2012}
An arbitrary set of constraints may

@@

\bibliography{HRI_internship_trajectory_planner_articles}
\bibliographystyle{IEEEtran}
